\documentclass{article}

\begin{document}
	\begin{center}
		\Huge Homework 0 Answers
	\end{center}
	
	\begin{enumerate}
		\huge
		\item Background
		
		\normalsize
		\begin{enumerate}
			\item Shawn Shacterman
			\item I am a junior transfer from American River College in Sacramento, CA. I enjoy hiking and rock climbing.
			\item It has been around a year since I finished linear algebra in community college, and I took a circuits course last semester. Despite this, I feel like I did not learn these subjects as well as I could have, and I am looking forward to receiving a much deeper exposure to these critical subject areas in EECS.
			\item I am not entirely sure, but I am sort of interested in machine learning and robotics (I am currently planning to take courses in both of these fields).
			\item I want to see some sort of electronic interface between the human brain and a digital circuit used for prosthetics (basically Captain Sliver from Treasure Planet, though 20 years might be a bit too optimistic for something like that).
			\item I have a fair amount of programming experience from coursework and some internships. I have 'technically' satisfied my lower division math requirements (they are definitely in need of some review though). I have also taken courses equivalent to the Physics 7 series at Berkeley and have taken an introductory circuits course (I think we were taking a cursory look at phasors and AC circuits by the end of the course).
			\item I primarily use Linux. I have a Windows Desktop that I also like to use but most of my programming is done on the Windows Ubuntu Subsystem.
			
		\end{enumerate}
		
		\huge
		\item Syllabus
		
		\normalsize
		\begin{enumerate}
			\item Midterm 1: (10/1, 8-10pm), Midterm 2: (11/2, 8-10pm)
			\item For exam accomodation, email the Head GSI at ee16a.staff@gmail.com during the first two weeks of the semester per university policy. In the case of an emergency, contact the Head GSI as soon as possible.
			\item "Homeworks are typically due on Friday night at 11:59 PM...self-grades will be due on the Tuesday following the homework deadline at 11:59 PM sharp."
			\item One homework drop is given for emergencies (lowest score).
			\item Half-credit is given to assignments turned in up to a week late.
			\item Complete the homework and turn it in on time. Turn in code and written solutions in the form of a .ipynb file and a .pdf file consisting of written-up solutions that also include an attached pdf "printout" of the code. Read the solutions when they are posted after the submission deadline. Complete the self-grade and turn it in on time.
			\item 8 points.
			\item None without a penalty and a maximum of three (more than three results in a failing grade).
		\end{enumerate}
		
		\huge
		\item Fun Fact
		
		\normalsize
		\begin{enumerate}
			\item Yellow
		\end{enumerate}
		
		\huge
		\item Homework Resources
		
		\normalsize
		\begin{enumerate}
			\item (vii) All of the Above
		\end{enumerate}
	\end{enumerate}


\end{document}